---
title: "WA Open Data Readiness Survey Visualizations"
output: html_notebook
---

Code authored by Bree Norlander. [ORCID:0000-0002-0431-4221](https://orcid.org/0000-0002-0431-4221)

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(waffle)
library(extrafont)
library(hrbrthemes)
```


```{r}
# Read in the data
PLOD <- read.csv("~/Data/PLOD-SurveyData.csv", stringsAsFactors = T)
```

```{r}
# For question one we will create a faceted waffle chart with 3 subsections as in the labels below:
Q1labels3 <- c(Q1_2 = "Our library provides \ninformation on community \nactivities and resources", 
               Q1_5 = "Our library offers guidance \non how to find or use \nnew information resources",  
               Q1_6 = "Our library offers guidance \non the use of \ninformation technologies")

# Created the faceted waffle chart
# following tutorial at https://github.com/hrbrmstr/waffle
PLOD %>%
  select(ResponseId, Q1_2, Q1_5, Q1_6) %>%
  # Pivot the data for viz purposes
  pivot_longer(cols = Q1_2:Q1_6,
               names_to = "Question",
               values_to = "Choice") %>%
  # set the order of the factor
  mutate(Choice = factor(Choice, 
                         levels = c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))) %>%
  group_by(Question) %>%
  # count will result in a new variable 'n'
  count(Choice) %>%
  ggplot(aes(fill = Choice, values = n)) +
    geom_waffle(color = "white", 
                size = .25, 
                n_rows = 4, 
                flip = TRUE) + # similar to coord_flip function, waffles are default horizontal
    facet_wrap(~Question, 
               nrow = 1, 
               strip.position = "bottom", 
               labeller=labeller(Question = Q1labels3) # use the custom labels assigned above
               ) + 
    scale_x_discrete() + 
    scale_y_continuous(labels = function(x) x * 4, # make this multiplyer the same as n_rows
                     expand = c(0,0)) +
    scale_fill_manual(name = NULL,
                      values = c("Strongly disagree" = "#F7FCF0",
                                 "Disagree" = "#CCEBC5",
                                 "Neutral" = "#7BCCC4",
                                 "Agree" = "#2B8CBE",
                                 "Strongly agree" = "#084081")
                      ) + 
  coord_equal() +
  theme(panel.grid = element_blank(), 
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.key = element_rect(fill = NA),
        # The two following lines make the background transparent
        panel.background = element_rect(fill = "transparent", colour = NA),
        plot.background = element_rect(fill = "transparent", colour = NA)
        ) +
  guides(fill = guide_legend(reverse = TRUE))

ggsave("~/Images/Q1_256_Facet_Waffle.png", bg = "transparent")
```

For Q3 (interests of local user community in following activities): create a refactored variable that buckets the answer choices as follows: unsure, unlikely, somewhat likely + likely, somewhat active + active, and highly likely (five categories instead of seven in that order) for simplicity on a particular chart. 

```{r}
# Add a re-factored variable that combines somewhat likely with likely AND somewhat active with active
PLOD <- PLOD %>% 
  mutate(Q3_1refactor = case_when(
    Q3_1 == "Unsure" ~ "Unsure",
    Q3_1 == "Unlikely" ~ "Unlikely",
    Q3_1 == "Somewhat likely" ~ "Likely",
    Q3_1 == "Likely" ~ "Likely",
    Q3_1 == "Somewhat active" ~ "Active",
    Q3_1 == "Active" ~ "Active",
    Q3_1 == "Highly Active" ~ "Highly Active"
  ),
  Q3_2refactor = case_when(
    Q3_2 == "Unsure" ~ "Unsure",
    Q3_2 == "Unlikely" ~ "Unlikely",
    Q3_2 == "Somewhat likely" ~ "Likely",
    Q3_2 == "Likely" ~ "Likely",
    Q3_2 == "Somewhat active" ~ "Active",
    Q3_2 == "Active" ~ "Active",
    Q3_2 == "Highly Active" ~ "Highly Active"
  ),
  Q3_3refactor = case_when(
    Q3_3 == "Unsure" ~ "Unsure",
    Q3_3 == "Unlikely" ~ "Unlikely",
    Q3_3 == "Somewhat likely" ~ "Likely",
    Q3_3 == "Likely" ~ "Likely",
    Q3_3 == "Somewhat active" ~ "Active",
    Q3_3 == "Active" ~ "Active",
    Q3_3 == "Highly Active" ~ "Highly Active"
  ),
  Q3_4refactor = case_when(
    Q3_4 == "Unsure" ~ "Unsure",
    Q3_4 == "Unlikely" ~ "Unlikely",
    Q3_4 == "Somewhat likely" ~ "Likely",
    Q3_4 == "Likely" ~ "Likely",
    Q3_4 == "Somewhat active" ~ "Active",
    Q3_4 == "Active" ~ "Active",
    Q3_4 == "Highly Active" ~ "Highly Active"
  ),
  Q3_5refactor = case_when(
    Q3_5 == "Unsure" ~ "Unsure",
    Q3_5 == "Unlikely" ~ "Unlikely",
    Q3_5 == "Somewhat likely" ~ "Likely",
    Q3_5 == "Likely" ~ "Likely",
    Q3_5 == "Somewhat active" ~ "Active",
    Q3_5 == "Active" ~ "Active",
    Q3_5 == "Highly Active" ~ "Highly Active"
  ),
  Q3_6refactor = case_when(
    Q3_6 == "Unsure" ~ "Unsure",
    Q3_6 == "Unlikely" ~ "Unlikely",
    Q3_6 == "Somewhat likely" ~ "Likely",
    Q3_6 == "Likely" ~ "Likely",
    Q3_6 == "Somewhat active" ~ "Active",
    Q3_6 == "Active" ~ "Active",
    Q3_6 == "Highly Active" ~ "Highly Active"
  ),
  Q3_7refactor = case_when(
    Q3_7 == "Unsure" ~ "Unsure",
    Q3_7 == "Unlikely" ~ "Unlikely",
    Q3_7 == "Somewhat likely" ~ "Likely",
    Q3_7 == "Likely" ~ "Likely",
    Q3_7 == "Somewhat active" ~ "Active",
    Q3_7 == "Active" ~ "Active",
    Q3_7 == "Highly Active" ~ "Highly Active"
  )
  )
```

```{r}
# Order the questions by most number of positive ("Likely", "Active", "Highly Active") answers to least
# Find out what that order is
Q3lvls <- PLOD %>% 
  select(ResponseId, Q3_1refactor:Q3_7refactor) %>%
  pivot_longer(cols = Q3_1refactor:Q3_7refactor,
               names_to = "Question",
               values_to = "Choice") %>%
  mutate(Choice = factor(Choice, levels = c("Unsure", "Unlikely", "Likely", "Active", "Highly Active"))) %>%
  group_by(Question, Choice) %>%
  tally() %>%
  filter(Choice %in% c("Likely", "Active", "Highly Active")) %>%
  summarise(total = sum(n)) %>%
  arrange(desc(total)) %>%
  select(Question)

# Q3labels will be used to label the facets
Q3labels <- c(Q3_1refactor = "Website Links", Q3_2refactor = "Reference Assist.", 
            Q3_3refactor = "Collections Dev.",  Q3_4refactor = "Professional Dev.",
            Q3_5refactor = "Community Programs",  Q3_6refactor = "Local Gov't Collab",
            Q3_7refactor = "Publish Data")

# Create a stacked bar chart of the count of responses
PLOD %>% 
  select(ResponseId, Q3_1refactor:Q3_7refactor) %>%
  pivot_longer(cols = Q3_1refactor:Q3_7refactor,
               names_to = "Question",
               values_to = "Choice") %>%
  mutate(Choice = factor(Choice, 
                         levels = c("Unsure", "Unlikely", "Likely", "Active", "Highly Active")
                         ),
         Question = factor(Question, levels = Q3lvls[[1]])) %>%
  ggplot(aes(x = Question, fill = forcats::fct_rev(Choice))) +
  geom_bar(stat="count", 
           color = "black", 
           size = 0.2, 
           position = "stack") +
  theme_bw() +
  scale_fill_manual(
    name = NULL,
    values = c("Unsure" = "#E0F3DB",
               "Unlikely" = "#A8DDB5",
               "Likely" = "#4EB3D3",
               "Active" = "#2B8CBE",
               "Highly Active" = "#084081")
    ) +
  scale_x_discrete(labels=Q3labels) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1), 
        axis.title.x=element_blank(),
        legend.title=element_blank()
        ) +
  ylab("Count of Responses") +
  labs(title = "Q.3", 
       subtitle = "Considering the interests of your local user community, indicate your library’s likely \nor current level of activity, on a scale ranging from “Unlikely” to become active to \n“Highly active” now.")

# Save chart
ggsave("~/Images/Q3_Stacked_Refactored_Count.png")
```

```{r}
# Stacked barchart normalized
PLOD %>% 
  select(ResponseId, Q3_1refactor:Q3_7refactor) %>%
  pivot_longer(cols = Q3_1refactor:Q3_7refactor,
               names_to = "Question",
               values_to = "Choice") %>%
  mutate(Choice = factor(Choice, 
                         levels = c("Unsure", "Unlikely", "Likely", "Active", "Highly Active")
                         ),
         Question = factor(Question, levels = Q3lvls[[1]])) %>%
  ggplot(aes(x = Question, fill = forcats::fct_rev(Choice))) +
  geom_bar(stat="count", 
           color = "black", 
           size = 0.2, 
           position = "fill") + #position fill for percents
  theme_bw() +
  scale_fill_manual(
    name = NULL,
    values = c("Unsure" = "#E0F3DB",
               "Unlikely" = "#A8DDB5",
               "Likely" = "#4EB3D3",
               "Active" = "#2B8CBE",
               "Highly Active" = "#084081")
    ) +
  scale_x_discrete(labels=Q3labels) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1), 
        axis.title.x=element_blank(),
        axis.title.y = element_blank(),
        legend.title=element_blank(),
        # The two following lines make the background transparent
        panel.background = element_rect(fill = "transparent", colour = NA),
        plot.background = element_rect(fill = "transparent", colour = NA)
        )

# Save chart
ggsave("~/Images/Q3_Stacked_Refactored_Pct.png", bg = "transparent")
```

Q7 visualize the overwhelming agreement. 

```{r}
Q7labels2 <- c(Q7_1 = "Aligns with Mission", Q7_2 = "Aligns with Community", 
            Q7_3 = "Aligns with Tech. Proficiency",  Q7_4 = "Difficult to Prioritize",
            Q7_5 = "Need New Funding",  Q7_6 = "Providing Leadership a Priority")

# https://github.com/hrbrmstr/waffle
PLOD %>%
  select(ResponseId, Q7_1:Q7_6) %>%
  pivot_longer(cols = Q7_1:Q7_6,
               names_to = "Question",
               values_to = "Choice") %>%
  mutate(Choice = factor(Choice, 
                         levels = c("Not sure", "Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))) %>%
  group_by(Question) %>% 
  count(Choice) %>%
  ggplot(aes(fill=Choice, values=n)) +
  geom_waffle(color = "white", 
              size=1.125, 
              n_rows = 6) +
  facet_wrap(~Question, 
             ncol=3, 
             labeller=labeller(Question = Q7labels2)) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  scale_fill_brewer(palette="GnBu") +
  coord_equal() +
  theme_enhance_waffle() + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks = element_blank(),
        legend.title=element_blank(),
        legend.key = element_rect(fill = NA),
        legend.text = element_text(hjust = 0, vjust = 1),
        # The two following lines make the background transparent
        panel.background = element_rect(fill = "transparent", colour = NA),
        plot.background = element_rect(fill = "transparent", colour = NA))

ggsave("~/Images/Q7_Facet_Waffle.png", bg = "transparent")
```

